### 2016-03-22 config/styles.inc.tex
Small consistency changes
Some figures reimported as TikZ + text on truncation
More figures CH03
More LPM-trunc figures

%% Colors
  \definecolor{tangored}{named}{TangoScarletRed1}
  \definecolor{tangoblue}{rgb}{0.203922,0.396078,0.643137}
  \definecolor{tangogreen}{named}{TangoChameleon2}
  \definecolor{tangogrey}{named}{TangoAluminium5}

  \definecolor{meas}{named}{TangoPlum2}

  \definecolor{goallight}{named}{TangoChameleon1}
  \definecolor{goal}{named}{TangoChameleon2}
  \definecolor{goaldark}{named}{TangoChameleon3}

  \definecolor{obtainedlight}{named}{TangoScarletRed1}
  \definecolor{obtained}{named}{TangoScarletRed2}
  \definecolor{obtaineddark}{named}{TangoScarletRed3}

  \definecolor{model}{named}{tangogrey}
  \definecolor{bg}{named}{TangoAluminium2}

\definecolor{model}{named}{black}
\definecolor{truesys}{named}{TangoAluminium5}
% \definecolor{truesys}{named}{TangoAluminium4} % from LRMHinf paper

\definecolor{linms}{named}{TangoSkyBlue3}
\definecolor{logms}{named}{TangoChameleon2}
\definecolor{qlogms}{named}{TangoPlum3}
\definecolor{clogms}{named}{TangoScarletRed3}
\definecolor{plogms}{named}{TangoOrange3}

\definecolor{sigmalinms}{named}{linms}
\definecolor{sigmaqlogms}{named}{qlogms}
\definecolor{sigmaclogms}{named}{clogms}

\definecolor{biaslinms}{named}{TangoSkyBlue1}
\definecolor{biasqlogms}{named}{TangoPlum1}
\definecolor{biasclogms}{named}{TangoScarletRed1}

\definecolor{dbacolor}{named}{TangoScarletRed2}
\definecolor{dbbcolor}{named}{TangoSkyBlue2}
\definecolor{dbccolor}{named}{TangoChameleon2}
\definecolor{dbdcolor}{named}{TangoOrange2}

\definecolor{compen}{rgb}{0.729,0.741,0.714}
\definecolor{signal}{named}{TangoSkyBlue2}
\definecolor{misalign}{named}{TangoScarletRed2}

\definecolor{first}{named}{TangoScarletRed2}
\definecolor{second}{named}{TangoOrange2}
\definecolor{third}{named}{TangoChameleon3}
\definecolor{fourth}{named}{TangoSkyBlue3}
\definecolor{fifth}{named}{TangoPlum1}
\definecolor{sixth}{named}{TangoChocolate2}

\definecolor{LPMTrunc}{named}{TangoSkyBlue2}
\definecolor{LPMTruncInit}{named}{TangoSkyBlue2}
\definecolor{RFIR}{named}{TangoScarletRed3}
\definecolor{RFIRInit}{named}{TangoScarletRed1}
\definecolor{existing}{named}{TangoChameleon3}
\definecolor{G0Hat}{named}{TangoOrange2}
\definecolor{GVXI}{named}{G0Hat}
\definecolor{reference}{named}{black}

\definecolor{heuristic}{named}{TangoPlum2}
\definecolor{observed}{named}{TangoOrange3}

\definecolor{best}{named}{TangoAluminium6}

\definecolor{G0HatFill}{named}{TangoOrange1}
\definecolor{GVXIFill}{named}{G0HatFill}
\definecolor{LPMTruncFill}{named}{TangoSkyBlue1}
\definecolor{RFIRFill}{named}{TangoScarletRed1}
\definecolor{existingFill}{named}{TangoChameleon1}
\definecolor{bestFill}{named}{TangoAluminium3}

\definecolor{FRFMean}{named}{TangoPlum3}
\definecolor{FRFSingle}{named}{TangoPlum1}
\definecolor{FRFNoise}{named}{TangoChocolate1}

\definecolor{LRM}{named}{TangoScarletRed3}
\definecolor{LPM}{named}{TangoSkyBlue2}
\definecolor{SA}{named}{TangoChameleon2}

\definecolor{validation}{named}{TangoChameleon2}

\definecolor{LPMshade}{named}{TangoSkyBlue1}
\definecolor{LRMshade}{named}{TangoScarletRed1}
\definecolor{refColor}{named}{TangoAluminium6}

\definecolor{frf}{named}{TangoButter3} %TODO: replace
\definecolor{param}{named}{TangoScarletRed2}

  \definecolor{bwfill}{named}{TangoAluminium1}
  \definecolor{bwline}{named}{TangoAluminium5}

  \definecolor{safezone}{named}{bwfill}

@@

%% marker styles

@@

\pgfplotsset{safezone/.style={fill=safezone,fill opacity=0.5,color=safezone}}

@@

\pgfplotsset{results/.style={solid,line width=0.7pt}}
\pgfplotsset{linmsres/.style={color=linms,results}}
\pgfplotsset{qlogmsres/.style={color=qlogms,results}}
\pgfplotsset{clogmsres/.style={color=clogms,results}}
\pgfplotsset{plogmsres/.style={color=plogms,results}}

%TODO: change these styles?
\pgfplotsset{linmsmeas/.style={color=linms,solid,line width=0.7pt}}
\pgfplotsset{qlogmsmeas/.style={color=qlogms,solid,line width=0.7pt}}
\pgfplotsset{clogmsmeas/.style={color=clogms,solid,line width=0.7pt}}
\pgfplotsset{plogmsmeas/.style={color=plogms,solid,line width=0.7pt}}

@@

\pgfplotsset{biasline/.style={densely dotted}}
\pgfplotsset{biaslinms/.style={color=biaslinms,linmsmarker,biasline}}
\pgfplotsset{biasqlogms/.style={color=biasqlogms,qlogmsmarker,biasline}}
\pgfplotsset{biasclogms/.style={color=biasclogms,clogmsmarker,biasline}}

@@

>>>>

%% Colors
  \colorlet{tangored}{TangoScarletRed1}
  \colorlet{tangoblue}{TangoSkyBlue2}
  \colorlet{tangogreen}{TangoChameleon2}
  \colorlet{tangogrey}{TangoAluminium5}

  \colorlet{meas}{TangoPlum2}

  \colorlet{goallight}{TangoChameleon1}
  \colorlet{goal}{TangoChameleon2}
  \colorlet{goaldark}{TangoChameleon3}

  \colorlet{obtainedlight}{TangoScarletRed1}
  \colorlet{obtained}{TangoScarletRed2}
  \colorlet{obtaineddark}{TangoScarletRed3}

  \colorlet{model}{tangogrey}
  \colorlet{bg}{TangoAluminium2}

\colorlet{model}{black}
\colorlet{truesys}{TangoAluminium5}
% \colorlet{truesys}{TangoAluminium4} % from LRMHinf paper

\colorlet{linms}{TangoSkyBlue3}
\colorlet{logms}{TangoChameleon2}
\colorlet{qlogms}{TangoPlum3}
\colorlet{clogms}{TangoScarletRed3}
\colorlet{plogms}{TangoOrange3}

\colorlet{sigmalinms}{linms}
\colorlet{sigmaqlogms}{qlogms}
\colorlet{sigmaclogms}{clogms}

\colorlet{biaslinms}{TangoSkyBlue1}
\colorlet{biasqlogms}{TangoPlum1}
\colorlet{biasclogms}{TangoScarletRed1}

\colorlet{dbacolor}{TangoScarletRed2}
\colorlet{dbbcolor}{TangoSkyBlue2}
\colorlet{dbccolor}{TangoChameleon2}
\colorlet{dbdcolor}{TangoOrange2}

\definecolor{compen}{rgb}{0.729,0.741,0.714}
\colorlet{signal}{TangoSkyBlue2}
\colorlet{misalign}{TangoScarletRed2}

\colorlet{first}{TangoScarletRed2}
\colorlet{second}{TangoOrange2}
\colorlet{third}{TangoChameleon3}
\colorlet{fourth}{TangoSkyBlue3}
\colorlet{fifth}{TangoPlum1}
\colorlet{sixth}{TangoChocolate2}

\colorlet{LPMTrunc}{TangoSkyBlue2}
\colorlet{LPMTruncInit}{TangoSkyBlue2}
\colorlet{RFIR}{TangoScarletRed3}
\colorlet{RFIRInit}{TangoScarletRed1}
\colorlet{existing}{TangoChameleon3}
\colorlet{G0Hat}{TangoOrange2}
\colorlet{GVXI}{G0Hat}
\colorlet{reference}{black}

\colorlet{heuristic}{TangoPlum2}
\colorlet{observed}{TangoOrange3}

\colorlet{best}{TangoAluminium6}

\colorlet{G0HatFill}{TangoOrange1}
\colorlet{GVXIFill}{G0HatFill}
\colorlet{LPMTruncFill}{TangoSkyBlue1}
\colorlet{RFIRFill}{TangoScarletRed1}
\colorlet{existingFill}{TangoChameleon1}
\colorlet{bestFill}{TangoAluminium3}

\colorlet{FRFMean}{TangoPlum3}
\colorlet{FRFSingle}{TangoPlum1}
\colorlet{FRFNoise}{TangoChocolate1}

\colorlet{LRM}{TangoScarletRed3}
\colorlet{LPM}{TangoSkyBlue2}
\colorlet{SA}{TangoChameleon2}

\colorlet{validation}{TangoChameleon2}

\colorlet{LPMshade}{TangoSkyBlue1}
\colorlet{LRMshade}{TangoScarletRed1}
\colorlet{refColor}{TangoAluminium6}

\colorlet{frf}{TangoButter3} %TODO: replace
\colorlet{param}{TangoScarletRed2}

  \colorlet{bwfill}{TangoAluminium1}
  \colorlet{bwline}{TangoAluminium5}

@@

@@

@@

%TODO: replace *res -> *meas
\pgfplotsset{results/.style={solid,line width=0.7pt}}
\pgfplotsset{linmsres/.style={color=linms,results}}
\pgfplotsset{qlogmsres/.style={color=qlogms,results}}
\pgfplotsset{clogmsres/.style={color=clogms,results}}
\pgfplotsset{plogmsres/.style={color=plogms,results}}

\pgfplotsset{measline/.style={solid,line width=0.7pt}}
\pgfplotsset{linmsmeas/.style={color=linms,measline}}
\pgfplotsset{qlogmsmeas/.style={color=qlogms,measline}}
\pgfplotsset{clogmsmeas/.style={color=clogms,measline}}
\pgfplotsset{plogmsmeas/.style={color=plogms,measline}}

@@

\pgfplotsset{biasline/.style={densely dotted}}
\pgfplotsset{biaslinms/.style={color=biaslinms,linmsmarker,biasline}}
\pgfplotsset{biasqlogms/.style={color=biasqlogms,qlogmsmarker,biasline}}
\pgfplotsset{biasclogms/.style={color=biasclogms,clogmsmarker,biasline}}
\pgfplotsset{biasplogms/.style={color=biasplogms,clogmsmarker,biasline}}

@@

%% Truncation
\pgfplotsset{truncationline/.style={dashdotdotted,line width=1.5pt,line join=round,line cap=round}}

\colorlet{FSmooth}{TangoScarletRed3}
\colorlet{expFit}{TangoSkyBlue3}
\colorlet{trunc}{clogms}

\pgfplotsset{FRFLPM/.style={color=LPM}}
\pgfplotsset{FRFtrunc/.style={color=trunc}}

\pgfplotsset{sigmaLPM/.style={sigmalinms}}
\pgfplotsset{sigmaTrunc/.style={sigmaplogms}}

\pgfplotsset{biasLPM/.style={biaslinms}}
\pgfplotsset{biasTrunc/.style={biasclogms}}

\pgfplotsset{histogramSmootherFTest/.style={ycomb,line width=1.5pt,fill=white!40!black,draw=white!40!black,area legend}}
\pgfplotsset{histogramSmootherExpFit/.style={ycomb,line width=1.5pt,fill=white!70!black,draw=white!70!black,opacity=0.8,area legend}}

\pgfplotsset{rmsOfSegment/.style={color=gray,line width=1pt,densely dotted}}
